Coalition Formation Algorithm of Prosumers in a Smart Grid Environment

### 2014-09-29 Article.tex
more recent newman refs

Presented in this way, the time-series clustering task seems very close to graph community detection. Communities in networks are indeed often seen as groups of nodes exhibiting high internal densities of links as well as a low density across communities, and several topology oriented techniques for finding communities are present in the litterature (\cite{Newmanb} \cite{Girvan2002} \cite{Newman}). For our purpose where decorrelation is the closeness notion, such algorithms tend to have some difficulties because only a few inclusions of very high correlations can strongly affect the stability of a coalition. However, local cliques, where all nodes are linked, provide uncorrelated groups of nodes. There exists greedy heuristics based on cliques in the litterature such as clique percolation \cite{Lancichinetti} which realizes local optimizations of a fitness function and results in overlaping community structures. Detection of overlapping communities is actually a very active field of research, especially in social networks where a person might belong to several communities.

>>>>

Presented in this way, the time-series clustering task seems very close to graph community detection. Communities in networks are indeed often seen as groups of nodes exhibiting high internal densities of links as well as a low density across communities, and several topology oriented techniques for finding communities are present in the litterature (\cite{Newman2013} \cite{Girvan2002} \cite{Newman2013_2}). For our purpose where decorrelation is the closeness notion, such algorithms tend to have some difficulties because only a few inclusions of very high correlations can strongly affect the stability of a coalition. However, local cliques, where all nodes are linked, provide uncorrelated groups of nodes. There exists greedy heuristics based on cliques in the litterature such as clique percolation \cite{Lancichinetti} which realizes local optimizations of a fitness function and results in overlaping community structures. Detection of overlapping communities is actually a very active field of research, especially in social networks where a person might belong to several communities.
